Containers and R: the Rockerverse and beyond

### 2019-09-09 manuscript.Rmd

## Introduction

@@

## Containerization and Rocker

@@

@@

### Bioconductor

@@

## Other containerisation platforms [NN]

## Non-Debian images [NN]

- Alpine images
- Images used by R-Hub (overlap with CI?)
- [Windows](https://github.com/nuest/rocker-win) [@nuest]
- https://github.com/jlisic/R-docker-centos

## Rocker for Research Compendia [@benmarwick]

@@

@@

## R versions [@ColinFay, @nuest]

## Discussion/outlook [all, please add bullet points]

@@

## Author contributions

>>>>

# Introduction

@@

# Containerization and Rocker

@@

# Container Images

@@

## Bioconductor

@@

## Images for (historic) R versions [@ColinFay, @nuest]

## Windows Images [@nuest]

- [rocker-win](https://github.com/nuest/rocker-win)
- is possible, only relevant in organisations with an existing Windows Server-based infrastructure, can meet policies then

## Non-Debian Linux images [NN]

- Alpine images
- [Images used by R-Hub](https://github.com/r-hub/rhub-linux-builders) (overlap with CI?)
- https://github.com/jlisic/R-docker-centos

# R Packages

@@

# Use cases and applications

@@

## Research Compendia [@benmarwick]

# Other containerisation platforms [NN]

# Discussion/outlook/conclusion [@all, please add bullet points]

@@

# Author contributions
